Draft

### 2022-06-13 draft/draft.qmd
created new qmd called draft

---
title: "Proposal"
subtitle: "STA 210 - Project"
author: "Bayes' Harem - Christina Wang, Kat Cottrell, David Goh, Ethan Song"
format: pdf
editor: source
editor_options: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Draft"
subtitle: "STA 210 - Project"
author: "Bayes' Harem - Christina Wang, Kat Cottrell, David Goh, Ethan Song"
format: pdf
editor: source
editor_options: 
  markdown: 
    wrap: 72
---
